### 2021-03-18 README.Rmd
added two examples for usage under README

Examples about how to navigate `dataaimsr` and interrogate the datasets can
be found on our [online vignettes][4].

>>>>

```{r, eval = FALSE}
# assumes that user already has API key saved to
# .Renviron
library(dataaimsr)

# summarised by series
# for all sites that contain data
# within a defined date range
sdf_b <- aims_data("temp_loggers", api_key = NULL,
                   summary = "summary-by-series",
                   filters = list("from_date" = "2018-01-01",
                                  "thru_date" = "2018-12-31"))

# downloads weather data from site Yongala
# within a defined date range
wdf_a <- aims_data("weather", api_key = NULL,
                   filters = list(site = "Yongala",
                                  from_date = "2018-01-01",
                                  thru_date = "2018-01-02"))
```

More comprehensive examples about how to navigate `dataaimsr` and interrogate
the datasets can be found on our [online vignettes][4].
